---
title: "phd_data"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{phd_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rvedata)
```

With the help of this package a simulated data set can be created for use in the context of risk equalization. The simulations are based on the tables published in the [PhD thesis](https://api.zotero.org/users/24775/publications/items/KBKWIQDJ/file/view) of [Piet Stam](https://www.pietstam.nl).

Call the function `phd_data` to create a simulated data set. This function has two parameters: `nobs` and `seed`. Set `nobs` to the number of observations that you want to create, it will default to 100 observations if you omit this argument. For ease of replication, set `seed` to any number that you like (and are able to remember). A random seed will apply if you omit this second argument.

Time for some basic examples. First create a data frame with 100 observations using a random seed:

```{r}
df <- phd_data()
```

To create a data frame with 1000 observations still using a random seed proceed as follows:

```{r}
df <- phd_data(1000)
```

And as a final introductory example, create a data frame with 1000 observations and set the seed to 1234:

```{r}
df <- phd_data(1000, 1234)
```
