---
title: "Run some OLS regressions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{run-ols-regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rvedata)
library(magrittr)
```

In order to run a regression with the `phd_data` that you created, first we create the sets of variables to build the regression formulas. Notice that we omit one category of the `gender_age` variable, assuming that we include an intercept when running the regression. Also, we omit a reference category for each other variable. Of course, this does not hold for the continuous variables `hprice`, `gpdist` and `hdist`.

```{r eval = FALSE}
# Expenditures
yvar <- "Y"
# Age
gender_age <- c(paste0("M_AGE", c(2:8)), paste0("F_AGE", c(1:8)))
# Insurance eligibility
incsrc <- paste0("INCSRC", c(1,3:6))
# Region
region <- paste0("REGION", c(1:9))
# PCGs
PCG <- paste0("PCG", c(1:12))
# DCGs
DCG <- paste0("DCG", c(1:13))
# Hospital output price (in 100 euro)
hprice <- c("hprice")
# Distance to nearest GP
gpdist <- c("gpdist")
# Distance to nearest hospital
hdist <- c("hdist")
```

Then we run a first regression with only `gender_age` included. Everything seems to look just fine.

```{r eval = FALSE}
xvars <- c(gender_age)

formula1 <- paste0(yvar, " ~ ", paste(xvars, collapse="+")) %>% 
  as.formula()

lm1 <- lm(formula = formula1, data = rvedata::example_phd_data)

summary(lm1)
```

The regression would look a bit different at first sight if we had included all categories of `gender_age`. Notice that the estimated coefficients in this regression are identical to those of the former regression if you add the estimated intercept to each estimated effect of `gender_age`.

```{r eval = FALSE}
xvars <- c("M_AGE1", gender_age)

formula2 <- paste0(yvar, " ~ 0 + ", paste(xvars, collapse="+")) %>% 
  as.formula()

lm2 <- lm(formula = formula2, data = rvedata::example_phd_data)

summary(lm2)
```

Let's move on and add the other risk adjusters. Notice that, as a consequence, the estimated coefficients for young people increase at the expense of older people. Why is that?

```{r eval = FALSE}
xvars <- c("M_AGE1", gender_age, incsrc, region, PCG, DCG)

formula3 <- paste0(yvar, " ~ 0 + ", paste(xvars, collapse="+")) %>% 
  as.formula()

lm3 <- lm(formula = formula3, data = rvedata::example_phd_data)

summary(lm3)
```

Finally, we check what happens if we include the N-type risk adjusters `hprice`, `gpdist` and `hdist` to the regression. Notice the `R-squared` value, what does this tell you?

```{r eval = FALSE}
xvars <- c("M_AGE1", gender_age, incsrc, region, PCG, DCG, hprice, gpdist, hdist)

formula4 <- paste0(yvar, " ~ 0 + ", paste(xvars, collapse="+")) %>% 
  as.formula()

lm4 <- lm(formula = formula4, data = rvedata::example_phd_data)

summary(lm4)
```

You may try for yourself to remove this so-called omitted variables bias from the regression. What did Schokkaert and Van de Voorde (2004) tell you to do?
